---
title: 'Part 1: binary logistic regression'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(jtools)

```

```{r}
penguins %>% 
  select(species, bill_length_mm:sex) %>% 
  ggpairs(aes(color = species))
```

Create subset w/ only Adelie & Chinstrap penguins
```{r}
adelie_chinstrap <- penguins %>% 
  filter(species %in% c("Adelie", "Chinstrap")) %>% 
  mutate(species = fct_drop(species)) # do this hw1?
```

Let's dataviz these two species: 
```{r}
ggplot(data = adelie_chinstrap, aes(x = body_mass_g,
                                    y = flipper_length_mm)) +
  geom_point(aes(color = sex)) +
  facet_wrap(~species)
```

Binary logistic regression - find probability based on several variables if a penguin based on our model is Adelie or Chinstrap (binning of data is basis for many machine learning techniques)

- body mass
- flipper length
- penguin sex
```{r}
adelie_chinstrap_blr <- glm(species ~
                              body_mass_g + flipper_length_mm + sex,
                            data = adelie_chinstrap,
                            family = "binomial") # On L side, link = log odds, 2 outcome vars
```

Take a look at outcomes:
```{r}
adelie_chinstrap_blr

summary(adelie_chinstrap_blr)

# Interpret coefficients: body mass (continuous measured var), L side = Chinstrap (2nd fct, Adelie = ref lvl), as body mass increases log-odds of being Chinstrap decrease
```

```{r}
ggplot(data = adelie_chinstrap,
       aes(x = species, y = flipper_length_mm)) +
  geom_jitter(aes(color = sex))
#Shows that as flipper length increases, odds of being Chinstrap increase
```

What are the actual probabilities of being Chinstrap for each of the existing observations in adelie_chinstrap df?
```{r}
blr_fitted <- adelie_chinstrap_blr %>% 
  broom::augment(type.predict = "response")
# Fitted value tells probability based on body mass/flipper length/sex that penguin is Chinstrap - most rows are right, some are wrong, dangerous to use for classification
```

Plotting fitted probabilities 
```{r}
ggplot(data = blr_fitted,
       aes(x = flipper_length_mm, y = .fitted)) +
  geom_point(aes(color = sex, pch = species)) + # Change pt style to actual species
  geom_smooth(aes(color = sex), se = FALSE) +
  labs(x = "Flipper length (mm)",
       y = "Probability of outcome Chinstrap")
```

Plot actual model fit based on different variables (flipper length, body mass):
```{r}
jtools::effect_plot(adelie_chinstrap_blr,
                    pred = body_mass_g,
                    y.label = "Probability of Chinstrap",
                    interval = TRUE) #Quick overview of how prob changes wrt model var
```

What's the probability a female penguin weighing 3410g w/ flipper length of 192mm is a Chinstrap?
```{r}
ex_1 <- predict(adelie_chinstrap_blr,
                data.frame(sex = "female",
                           body_mass_g = 3410,
                           flipper_length_mm = 192),
                type = "response") # Converts log-odds to actual probability

ex_1
```

